Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-25 tex/results.tex
typo fix

The constraints of mesh generation mean that we have only loose control on triangle density. Our meshes for the rectangular prism all have densities like in the coarse case of the grid-dependence study of section \ref{sec:independence}, or finer.
For the third dimension, we needed to choose a value that represents ``infinity.'' To achieve this, we studied the effects of 
elongating the cylinder to the third dimension. In Figure \ref{fig:ext_y_14}, we present the results for two different
values of the length in the third dimension, $y=1344$ nm ($2\times a$) and $y=2688$ nm ($4\times a$). We see that as we make $y$ longer, the 
intensity of some peaks decreases, due to the fact that some of the peaks are associated to this component. Therefore, 
from now on we use $y=2688$ nm. We could have increased this value more, but the
simulations then become computationally more expensive and we would still have the 3D effects in the model.

>>>>

The constraints of mesh generation mean that we have only loose control on triangle density. Our meshes for the rectangular prism all have densities like in the coarse case of the grid-independence study of sub-section \ref{sec:independence}, or finer.
For the third dimension, we needed to choose a value that represents ``infinity.'' To achieve this, we studied the effects of 
elongating the cylinder to the third dimension. In Figure \ref{fig:ext_y_14}, we present the results for two different
values of the length in the third dimension, $y=1344$ nm ($2\times a$) and $y=2688$ nm ($4\times a$). We see that as we make $y$ longer, the 
intensity of some peaks decreases, due to the fact that some of the peaks are associated to this component. Therefore, 
from now on we use $y=2688$ nm. We could have increased this value more, but the
simulations then become computationally more expensive and we would still have the 3D effects in the model.
